---
title: "Literature review: Historiography in 2020"
author: "Robert Z. Selden, Jr."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: book.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Historiography

This literature review was generated as a means of illustrating recent peer-reviewed publications in historiography. The dataset used in this analysis was harvested from [Scopus](https://www.elsevier.com/en-in/solutions/scopus), includes all publications returned for the query **_historiography_**, for which the results were then limited to 2020, and only those publications in the humanities. In total, 1,759 documents were returned, the analysis leverages the `bibliometrix` package in the R environment, and is reproducible.

```{r bibliometrix, echo=TRUE, warning=FALSE}
# install
#devtools::install_github("massimoaria/bibliometrix")

# load
library(here)
library(bibliometrix)
library(reshape2)
library(ggplot2)

# build data frame
df <- convert2df(file = "scopus.bib", 
                 dbsource = "scopus", 
                 format = "bibtex")
```

## Descriptive analysis

```{r summary, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
results <- biblioAnalysis(df, 
                          sep = ";")
options(width = 100)
s <- summary(object = results, 
             k = 20, 
             pause = FALSE)

# plot attributes
plot(x = results, 
     k = 20, 
     pause = FALSE)
```

### Attributes of the local network

```{r local.attr, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# calculate citations in local network
CR <- localCitations(df, sep = ";")

# top 20 cited authors in local network
CR$Authors[1:20,]

# top 20 cited papers in local network
CR$Papers[1:20,]
```

## Most cited

### Most cited articles

```{r most.cited.refs, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# most cited references in global network
mcr <- citations(df, 
                 field = "article", 
                 sep = ";")

cbind(mcr$Cited[1:20])
```

### Most cited authors

```{r most.cited.auths, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# most cited authors in global network
mcr <- citations(df, 
                 field = "author", 
                 sep = ";")

cbind(mcr$Cited[1:20])
```

### Author dominance ranking

```{r auth.dom, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
dom <- biblioAnalysis(df)
dom.r <- dominance(dom)
dom.r
```

## Intellectual structure

### Author co-citation

Co-citation analysis is the most commonly used bibliometric analysis method [@RN20999], and is defined as two publications that are cited together in one article [@RN21000].

```{r auth.co.cite, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# extract author names from reference items
df <- metaTagExtraction(df,
                        Field = "CR_AU")

# author co-citation network
auth.co.mat <- biblioNetwork(df, 
                             analysis = "co-citation", 
                             network = "authors", 
                             sep = ";")

# network plot
auth.co.net = networkPlot(auth.co.mat, 
                          n = 50, 
                          Title = "Author Co-Citation Network", 
                          type = "fruchterman", 
                          size = 20, 
                          size.cex = T, 
                          remove.multiple = FALSE, 
                          labelsize = 0.5, 
                          edgesize = 8, 
                          edges.min = 3, 
                          remove.isolates = TRUE)
```

### Bibliographic coupling

Coupling is a similarity measure that uses citation analysis to illustrate a similarity relationship between documents. Bibliographic coupling occurs when two works reference a common third work in their bibliographies.

```{r man.coup, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# bibliographic coupling network
bib.co.mat <- biblioNetwork(df, 
                            analysis = "coupling", 
                            network = "references", 
                            sep = ";")

# network plot
bib.co.net = networkPlot(bib.co.mat, 
                         n = 40, 
                         Title = "Manuscript Coupling Network", 
                         type = "fruchterman", 
                         size = 20, 
                         size.cex = T, 
                         remove.multiple = FALSE, 
                         labelsize = 0.4, 
                         edgesize = 10, 
                         edges.min = 3, 
                         remove.isolates = TRUE)
```

### ID and DE keyword associations

```{r key.assocx, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
list <- keywordAssoc(df, 
                     sep = ";", 
                     n = 10)

list[[1]][1:10]
```

## Conceptual structure

### Co-word analysis

The co-word analysis maps the conceptual structure of a research domain using the co-occurrence of author keywords in the bibliographic collection.

#### Author's keywords

```{r co.word, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# using authors keywords
cw <- conceptualStructure(df, 
                          field = "DE", 
                          method = "MDS", 
                          minDegree = 2, 
                          clust = "auto", 
                          stemming = FALSE, 
                          labelsize = 6, 
                          documents = 313)
```

#### Publisher's keywords

```{r co.word2i, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# using publishers keywords
cw <- conceptualStructure(df, 
                          field = "ID", 
                          method = "MDS", 
                          minDegree = 2, 
                          clust = "auto", 
                          stemming = FALSE, 
                          labelsize = 4, 
                          documents = 313)
```

## Thematic mapping

From [@RN20996, 150-151]:

* Themes in the upper-right quadrant are both well developed and important for the structuring ofa research field. They are known as the motor-themes of the specialty, given that they present strong centrality and high density. The placement of themes in this quadrant implies that they are related externally to concepts applicable to other themes that are conceptually closely related.
* Themes in the upper-left quadrant have well developed internal ties but unimportant external ties and so are of only marginal importance for the field. These themes are very specialized and peripheral in character.
* Themes in the lower-left quadrant are both weakly developed and marginal. The themes of this quadrant have low density and low centrality, mainly representing either emerging or disappearing themes.
* Themes in the lower-right quadrant are important for a research field but are not developed. So, this quadrant groups transversal and general, basic themes.

### Authors' keywords

```{r thematic.map, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# keyword map
map1 = thematicMap(df, 
                   field = "DE", 
                   n = 1000, 
                   minfreq = 10, 
                   stemming = FALSE, 
                   size = 0.8, 
                   n.labels = 1, 
                   repel = TRUE)
# plot map
plot(map1$map)
```

### Publisher's keywords

```{r thematic.map2b, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# keyword map
map2 = thematicMap(df, 
                   field = "ID", 
                   n = 1000,
                   minfreq = 2, 
                   stemming = FALSE, 
                   size = 0.8, 
                   n.labels = 1, 
                   repel = TRUE)
# plot map
plot(map2$map)
```

## Social structure

### Author collaboration 

Scientific collaborations are plotted where nodes are authors and links are co-authorships, illustrating collaborations between authors.

```{r auth.collab, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# author collaboration network
auth.collab <- biblioNetwork(df, 
                             analysis = "collaboration", 
                             network = "authors", 
                             sep = ";")

# network plot
auth.collabnet = networkPlot(auth.collab, 
                             n = 100, 
                             Title = "Author Collaboration", 
                             type = "fruchterman", 
                             size = 6, 
                             size.cex = T, 
                             edgesize = 2, 
                             labelsize = 0.4, 
                             remove.isolates = TRUE)
```

### Edu collaboration

Scientific collaborations are plotted where nodes are institutions and links are co-authorships, illustrating collaborations between institutions.

```{r edu.network, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# author collaboration network
edu.collab <- biblioNetwork(df, 
                            analysis = "collaboration", 
                            network = "universities",
                            sep = ";")

# network plot
edu.collabnet = networkPlot(edu.collab, 
                            n = 75, 
                            Title = "Edu Collaboration", 
                            type = "fruchterman", 
                            size = 10, 
                            size.cex = T, 
                            edgesize = 2, 
                            labelsize = 0.4, 
                            remove.isolates = TRUE)
```

### Country collaboration

```{r count.collab, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# country collaboration network
count <- metaTagExtraction(df, 
                           Field = "AU_CO", 
                           sep = ";")

cmat <- biblioNetwork(count, 
                      analysis = "collaboration", 
                      network = "countries", 
                      sep = ";")
# network plot
cnet = networkPlot(cmat, 
                    n = dim(cmat)[1], 
                    Title = "Country Collaboration", 
                    type = "fruchterman", 
                    size = 15, 
                    size.cex = T, 
                    edgesize = 1, 
                    labelsize = 0.6, 
                    remove.isolates = TRUE, 
                    cluster = "none")
# end of code
```
